Missing links and the topological robustness of food webs

### 2022-09-20 manuscript/ms_C3_v2.Rmd
update

keywords:
  - connectance
  - ABC
  - ADBM
  - food web
  - extinction
  - uncertainty
header-includes:
  - \usepackage{lineno}
  - \linenumbers
  - \usepackage {amsmath}
  - \setlength\parindent{24pt}
  - \usepackage{setspace}\doublespacing
# indent: true
mainfont: Times New Roman
bibliography: bibliography.bib
biblio-style: biblatex
output:
  rticles::arxiv_article:
    keep_tex: true
---

>>>>

keywords:
  - connectance
  - ABC
  - ADBM
  - food web
  - extinction
  - uncertainty
header-includes:
  - \usepackage{lineno}
  # - \linenumbers
  - \usepackage {amsmath}
  - \setlength\parindent{24pt}
  - \usepackage{setspace}\doublespacing
# indent: true
mainfont: Times New Roman
bibliography: bibliography.bib
biblio-style: biblatex
output:
  rticles::arxiv_article:
    keep_tex: true
---
